---
title: "PA3"
author: "Eileen Blum"
date: "`r Sys.Date()`"
output: 
  html_document: 
    highlight: haddock
    theme: yeti
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#EDA
##1. Data
Load the dataset of your choice and get information about its structure
```{r, pa3_setup, echo=TRUE, message=FALSE, warning=FALSE}
library(languageR)
library(tidyverse)
data(package = "languageR")
str(durationsGe)
```

```{r}
View(durationsGe)
```

##2. Tidy 
Tidy the dataset (every variable gets a column, every observation occupies a single row), if necessary.
```{r, warning=FALSE}
my_durGe <- durationsGe %>%
my_durGe %>%
  select(-YearOfBirth) %>%
  View() 
```

##3. Descriptive Statistics
Calculate descriptive statistics of your choice.
```{r}
my_durGe %>%
select(., NumberSegmentsOnset, DurationOfPrefix) %>%
  cor.test(my_durGe$NumberSegmentsOnset, my_durGe$DurationOfPrefix)
```
```{r}
my_durGe %>%
select(., Frequency, SpeechRate) %>% 
  cor.test(my_durGe$Frequency, my_durGe$SpeechRate)
```

##4. Model
Select two continuous variables and fit a model to the data (bivariate regression).
```{r, pa3_model}
durGe_fit <- lm(DurationOfPrefix ~ SpeechRate, data = my_durGe)
summary(durGe_fit)
```

```{r}
confint(durGe_fit)
```
```{r}
Slope: `r coefficients(durGe_fit)[2]`, CI: LB: `r confint(my_fit)[1, c(1,2)]`
coefficients(durGe_fit)
```

##5. Plot
Generate a plot that includes a regression line.
```{r, pa3_plot}
my_durGe %>%
ggplot(., aes(x = SpeechRate, y = DurationOfPrefix)) +
    geom_point() +
    geom_smooth(method = 'lm')
```

##6. Observations
Write up some general observations (1-2 paragraphs max)

